### 2016-01-20 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
More post evolution edits

Fig1 <- ggplot(temp,
       aes(x = CatchYear,
           y = TLKBmean,
           col = Season)) +
  ylab('Log telomere length (kb)') + 
  xlab('Lay Year') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 14), 
        axis.text.y = element_text(size = 14), 
        axis.title.y = element_text(size = 16,vjust=0.8),
        axis.title.x = element_text(size = 16),
        legend.position = 'none') +
  geom_pointrange(aes(ymin=TLKBmean-TLKBse,ymax=TLKBmean+TLKBse)) +
  geom_line()+
  scale_color_manual(values = c('black',grey(0.5)))

@@

pdf('Figures/Figure 1.pdf',
    width = 6,
    height = 4,
    paper = 'a4')
Fig1
dev.off()

@@

####################
Fig1 <- ggplot(dd,
       aes(x = Fledged,
           y = LogTL,
           col = Season)) +
  ylab('Telomere length (kb)') + 
  xlab('Lay Year') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 14), 
        axis.text.y = element_text(size = 14), 
        axis.title.y = element_text(size = 16,vjust=0.8),
        axis.title.x = element_text(size = 16),
        legend.position = 'none') +
  geom_pointrange(aes(ymin=TLKBmean-TLKBse,ymax=TLKBmean+TLKBse)) +
  geom_line()+
  scale_color_manual(values = c('black',grey(0.5)))

@@

pdf('Figures/Figure 1.pdf',
    width = 6,
    height = 4,
    paper = 'a4')
Fig1
dev.off()

@@

#####################

#Run the model
lm2 <- lmer(LogTL ~ Fledged + Tarsus + Helper + GroupSize + Sex +Tarsus + BodyMass  + cenTQ  + (1|LayYear) + (1|PlateID),
            data = juv,
            REML = FALSE)

@@

#Sort out row/col names
nams <- rownames(table2)
nams[nams == 'cenTarsus'] <- 'Tarsus'
nams[nams == 'cenNonHelper'] <- 'Non helpers'
nams[nams == 'SexMales'] <- 'Sex'
nams[nams == 'cenTQ'] <- 'TQ'
nams[nams == 'cenHelper'] <- 'Helpers'
nams[nams == 'cenHelper:FledgedFledglings'] <- 'Ageclass x Helpers'
nams[nams == 'cenNonHelper:FledgedFledglings'] <- 'Ageclass x Non helpers'
nams[nams == 'cenTarsus:FledgedFledglings'] <- 'Ageclass x Tarsus'
nams[nams == 'cenTQ:FledgedFledglings'] <- 'Ageclass x TQ'
nams[nams == 'FledgedFledglings:SexMales'] <- 'Ageclass x Sex'
nams[nams == 'FledgedFledglings'] <- 'Ageclass'

@@

Fig3 <- forestplot(table2) +
  annotate('text',label = 'A',x=0.6,y=0.1)

pdf('Figures/Figure 2.pdf',
    width = 8,
    height = 8,
    paper = 'a4')
Fig3
dev.off()

@@

```{r Figure 3,fig.height=8,fig.width=4}

s1 <- survfit(Surv(time = Lifespan+1, event = Died)~TLF, data = chickall)
Fig3A <- ggsurv(s1,plot.cens=F,lty.est=c(1,2)) + 
  theme_classic() +
  ylab('Proportion survived') + 
  xlab('Age (years)') + 
  xlim(c(0,15)) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 14), 
        axis.text.y = element_text(size = 14), 
        axis.title.y = element_text(size = 16,vjust=0.8),
        axis.title.x = element_text(size = 16),
        legend.position = 'none') +
  scale_colour_manual(name = 'TL',
                      values = c('black',grey(0.5))) +
  guides(colour=F) +
  annotate('text',x=0.5,y=1.1,label='A')

###########################################
s2 <- survfit(Surv(time = Lifespan+1, event = Died)~TLF, data = FlSAall)
Fig3B <- ggsurv(s2,plot.cens=F,lty.est=c(1,2)) + 
  theme_classic() +
  ylab('Proportion survived') + 
  xlab('Age (years)') + 
  xlim(c(0,15)) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 14), 
        axis.text.y = element_text(size = 14), 
        axis.title.y = element_text(size = 16,vjust=0.8),
        axis.title.x = element_text(size = 16),
        legend.position = 'none') +
  scale_colour_manual(name = 'TL',
                      values = c('black',grey(0.5))) +
  guides(colour=F) +
  annotate('text',x=0.5,y=1.1,label='B')

pdf('Figures/Figure 3.pdf',
    width = 4,
    height = 8,
    paper = 'a4')
multiplot(Fig3A,Fig3B)
dev.off()

@@

>>>>

temp <- dd
temp <- subset(temp,Age<14)

ddFig1A <- ddply(temp,
                 .(Age),
                 summarize,
                 TL = mean(LogTL),
                 TLse = se(LogTL),
                 n = length(LogTL))

Fig1A <- ggplot(ddFig1A,
       aes(x = Age,
           y = TL)) +
  ylab('Log telomere length (kb)') + 
  xlab('Age (years)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 14), 
        axis.text.y = element_text(size = 14), 
        axis.title.y = element_text(size = 16,vjust=0.8),
        axis.title.x = element_text(size = 16),
        legend.position = 'none') +
  geom_pointrange(aes(ymax=TL+TLse,ymin=TL-TLse))+
  geom_line()+
  annotate('text',label = paste0('(',ddFig1A$n,')'),x = ddFig1A$Age,y = 3.3,size=3)+
  annotate('text',label='A',x = 0,y = 3.8)

####################
ss <- table(juv$Fledged)

Fig1B <- ggplot(juv,
       aes(x = Fledged,
           y = LogTL)) +
  ylab('Telomere length (kb)') + 
  xlab('') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 14), 
        axis.text.y = element_text(size = 14), 
        axis.title.y = element_text(size = 16,vjust=0.8),
        axis.title.x = element_text(size = 16),
        legend.position = 'none') +
  geom_boxplot(notch=T)+
  scale_color_manual(values = c('black',grey(0.5))) +
  annotate('text',label = paste0('(',ss,')'),x = c(1:2),y = 2.85)+
  annotate('text',label='B',x = 0.5,y = 4.5)

@@

pdf('Figures/Figure 1.pdf',
    width = 9,
    height = 3,
    paper = 'a4r')
multiplot(Fig1A,Fig1B,layout = matrix(c(1,1,1,1,2,2,2),nrow=1))
dev.off()

@@

ss <- temp$n

Fig2 <- ggplot(temp,
       aes(x = LayYear,
           y = TLKBmean) +
  ylab('Log telomere length (kb)') + 
  xlab('Lay Year') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 14), 
        axis.text.y = element_text(size = 14), 
        axis.title.y = element_text(size = 16,vjust=0.8),
        axis.title.x = element_text(size = 16),
        legend.position = 'none') +
  geom_pointrange(aes(ymin=TLKBmean-TLKBse,ymax=TLKBmean+TLKBse)) +
  geom_line()+
  annotate('text',label=paste0('(',ss,')'),x = temp$LayYear,y = 3.4,size = 4)

@@

pdf('Figures/Figure 2.pdf',
    width = 8,
    height = 4,
    paper = 'a4r')
Fig2
dev.off()

adults2 <- subset(adults,Age>0)

mymean <- tapply(adults2$LogTL,adults2$CatchYear,mean)
myse <- tapply(adults2$LogTL,adults2$CatchYear,se)
myn <- tapply(adults2$LogTL,adults2$CatchYear,length)

ddFig2B <- data.frame(TL = mymean, TLse = myse, n = myn,LayYear = as.numeric(names(mymean)))

ddFig2B <- subset(ddFig2B,n>5)

ss <- ddFig2B$n

Fig2 <- ggplot(ddFig2B,
       aes(x = LayYear,
           y = TL)) +
  ylab('Log telomere length (kb)') + 
  xlab('Lay Year') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 14), 
        axis.text.y = element_text(size = 14), 
        axis.title.y = element_text(size = 16,vjust=0.8),
        axis.title.x = element_text(size = 16),
        legend.position = 'none') +
  geom_pointrange(aes(ymin=TL-TLse,ymax=TL+TLse)) +
  geom_line()+
  annotate('text',label=paste0('(',ss,')'),x = ddFig2B$LayYear,y = 3.3,size = 4)

@@

#####################
#3A
#####################

#Run the model
lm2 <- lmer(LogTL ~ Fledged + Tarsus + Helper + NonHelper + Sex + Tarsus + BodyMass  + cenTQ  + Season + (1|LayYear) + (1|PlateID) + (1|BirdID),
            data = juv,
            REML = FALSE)

@@

#Sort out row/col names
nams <- rownames(table2)
nams[nams == 'NonHelper'] <- 'Non helpers'
nams[nams == 'SexMales'] <- 'Sex'
nams[nams == 'cenTQ'] <- 'TQ'
nams[nams == 'Helper'] <- 'Helpers'
nams[nams == 'BodyMass'] <- 'Body mass'
nams[nams == 'FledgedFledglings'] <- 'Age class'
nams[nams == 'SeasonWinter'] <- 'Season'

@@

Fig3A <- forestplot(table2)

#####################
#3B
#####################

#Run the model
lm2 <- lmer(TROC ~ Fledged + Tarsus + Helper + NonHelper + Sex + Tarsus + BodyMass  + cenTQ  + Season + LogTL + (1|LayYear),
            data = Loss,
            REML = FALSE)

#Sort out row/col names
nams <- rownames(table2)
nams[nams == 'NonHelper'] <- 'Non helpers'
nams[nams == 'SexMales'] <- 'Sex'
nams[nams == 'cenTQ'] <- 'TQ'
nams[nams == 'Helper'] <- 'Helpers'
nams[nams == 'BodyMass'] <- 'Body mass'
nams[nams == 'FledgedFledglings'] <- 'Age class'
nams[nams == 'SeasonWinter'] <- 'Season'
nams[nams == 'LogTL'] <- 'Initial TL'

Fig3B <- forestplot(table2)

pdf('Figures/Figure 3.pdf',
    width = 7,
    height = 8,
    paper = 'a4')
multiplot(Fig3A,Fig3B)
dev.off()

@@

```{r Figure 4}

ss <- c(tapply(juv$LogTL,list(juv$Season,juv$Fledged),length))

Fig4A <- ggplot(juv,
       aes(x = Fledged,
           y = LogTL,
           fill=Season)) +
  ylab('Telomere length (kb)') + 
  xlab('') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 14), 
        axis.text.y = element_text(size = 14), 
        axis.title.y = element_text(size = 16,vjust=0.8),
        axis.title.x = element_text(size = 16),
        legend.position = 'none') +
  geom_boxplot(notch=F)+
  scale_fill_manual(values = c('white',grey(0.5))) +
  annotate('text',label='A',x = 0.5,y = 4.5) +
  annotate('text',label = paste0('(',ss,')'),x=c(0.8,1.2,1.8,2.2),y = 2.8)

Fig4B <- ggplot(juv,
       aes(x = Tarsus,
           y = LogTL,
           col = Fledged)) +
  ylab('Telomere length (kb)') + 
  xlab('') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 14), 
        axis.text.y = element_text(size = 14), 
        axis.title.y = element_text(size = 16,vjust=0.8),
        axis.title.x = element_text(size = 16),
        legend.position = 'none') +
  geom_point()+
  scale_colour_manual(values = c('black',grey(0.5))) +
  annotate('text',label='B',x = 17.5,y = 4.5) +
  stat_smooth(method = 'lm')

pdf('Figures/Figure 4.pdf',
    width = 4,
    height = 8,
    paper = 'a4')
multiplot(Fig4A,Fig4B)
dev.off()

@@

```{r Figure 5}
s1 <- survfit(Surv(time = Lifespan+1, event = Died)~TLF, data = juv)
Fig5 <- ggsurv(s1,plot.cens=F,lty.est=c(1,2)) + 
  theme_classic() +
  ylab('Proportion survived') + 
  xlab('Age (years)') + 
  xlim(c(0,15)) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 14), 
        axis.text.y = element_text(size = 14), 
        axis.title.y = element_text(size = 16,vjust=0.8),
        axis.title.x = element_text(size = 16),
        legend.position = 'none') +
  scale_colour_manual(name = 'TL',
                      values = c('black',grey(0.5))) +
  guides(colour=F)

pdf('Figures/Figure 5.pdf',
    width = 4,
    height = 4,
    paper = 'a4')
Fig5
dev.off()
